The Heavy Photon Search Test Detector

### 2014-04-03 hps-testrun-nim.tex
Stepans comments

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at an energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in a final state particle within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
which have radiated in the target disperse horizontally in the field of the analyzing magnet. Together 
they constitute a "wall of flame" which must be completely avoided. Accordingly, 
the apparatus is split vertically to avoid a "dead zone", the region within $\pm 15$~mrad of the beam 
plane. In addition, the beam is transported in vacuum through the tracker to minimize beam-gas 
interaction backgrounds. Even with these precautions, the occupancies of sensors near the beam 
plane are high, dominated by the
multiple Coulomb scattering of the primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
The trigger comes from a highly-segmented  PbWO$_{4}$ crystal calorimeter located just downstream 
of the dipole magnet. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

The silicon tracking and vertexing detector for HPS Test, or SVT, resides in a vacuum 
chamber inside the pair spectrometer analyzing magnet in Hall B at JLab. The SVT has five 
measurement stations, or ``layers,'' beginning10 cm downstream of the target. Each layer 
comprises a pair of closely-spaced silicon microstrip sensors responsible for measuring a single 
coordinate, or ``view.'' Introduction of a small (50 or 100~mrad) stereo angle between the two 
sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
of the detecto. In order to accommodate the dead zone, the 
SVT is built in two halves that are approximately mirror reflections of one another about the plane of the 
nominal electron beam.  Each layer in one half is supported on a common support plate with 
independent cooling and readout.

@@

\section{The HPS Test Run Beamline}
The HPS Test run studied multiple Coulomb scattering of electrons and positrons from 
bremsstrahlung photons produced in the Hall B tagged photon facility. 
Figure~\ref{fig:hpstest_layout} shows the layout of 
the setup on the beam line. The SVT was installed inside the Hall B pair 
spectrometer magnet (PS) vacuum chamber with the ECal mounted downstream of it. Both the 
SVT and the ECal were retracted off the beam plane compared to nominal electron beam runing to 
allow clean passage of the photon beam through the system. 
\begin{figure}[]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

The photon beam was generated in the interaction of $5.5$~GeV electrons with a $10^{-4}~X_0$ 
gold radiator located $\approx~9$~m upstream of the PS. The primary beam and scattered 
electrons are deflected away from detectors by the dipole magnet of the photon tagging system. 
During the dedicated HPS Test run period, the collimated (6.4~mm diameter), photon beam passes 
through the aluminum PS pair converter and later the HPS system as illustrated in 
Fig.~\ref{fig:schematic_testrun_vs_erun}.
\begin{figure}[]
\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
\caption{\small{Illustrative comparison of HPS Test run photon beam compared to the HPS electron 
beam.}}
\label{fig:schematic_testrun_vs_erun}
\end{figure}
The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.

@@

The ECal module shown in Fig.~\ref{fig:ecal-module} is based on a tapered 160~mm long 
lead-tungstate (PbWO$_{4}$) crystal with a $13.3\times13.3$~mm$^2$ ($16\times16$~mm$^2$) front 
(rear) face wrapped in VM2000 multilayer polymer mirror film. 
\begin{figure}[]
\begin{center}
{\small
\includegraphics[width=7cm]{figures/ecal-module-schematic.png}
\caption{Schematic vied of an ECal module.}
\label{fig:ecal-module}
}
\end{center}
\end{figure}
The scintillation light, approximately $X$ photoelectrons/MeV, is readout by a 
5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. 
The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which 
provide factor of 2000 amplification of the APD signal.

\subsection{Layout}
Similar to the SVT, the ECal is built in two separate halves that are mirror reflections of one another 
about the plane of the nominal electron beam to avoid interfering with the 15~mrad "dead zone". 
As shown in Fig.~\ref{fig:ecal}, the 221 modules, supported by aluminum support frames, in each half 
are arranged in rectangular formation with 5 layers and 46 crystals/layer except for the layer closest to 
the beam where 9 modules were removed to allow a larger opening for the outgoing electron and 
photon beams. Each half was enclosed in a temperature controlled box ($<1^{\circ}$~F stability and 
$<4^{\circ}$~F uniformity) to stabilize the crystal light yield and the operation of the APDs and its 
preamplifiers. 
Four printed circuit boards mounted on the backplane penetrated the enclosure and was used to 
supply the $\pm 5$~V operating voltage for the preamplifiers, 400~V bias voltage to the APDs, and to 
read out signals from the APDs. Each half of the ECal was divided into 12 bias voltage groups with a 
gain uniformity of about 20\%.

@@

\subsection{Signal readout}
\label{sec:fadc}
After a 2:1 signal splitter, $1/3$ of an amplified APD signal ($2/3$ is sent to a timing module) is fed to a 
single channel of a JLab flash ADC (FADC) board~\cite{fadc}.
%\begin{figure}[]
%\begin{center}
%{\small
%\includegraphics[width=4cm]{figures/FADC250_Photo_001.jpg}
%\caption{The JLab FADC250 VXS module.}
%\label{fig:fadc}
%}
%\end{center}
%\end{figure}
The FADC boards are high speed VXS modules digitizing up to 16 APD signals 
at 250~MHz and storing samples in 8~$\mu$s deep pipelines with 12-bit resolution. 
When a trigger is received, the part 
of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
threshold (for the Test run this was set to $\approx70$~MeV) are 
summed and stored in a 17-bit register for readout. In addition a 4~ns resolution timestamp of the 
threshold crossing is reported in the readout for each pulse.
This scheme significantly compresses the data output of the FADC. During offline data analysis, a 
calibrated pedestal value is subtracted to obtain the actual summed energy.
Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test run to read out the top 
(bottom) half of the ECal.
In the Test run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules were 
disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
excessive noise) and 18 were masked offline due to noise. 
%\begin{figure}[]
%\begin{center}
%{\small
%\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
%\caption{The two different readout modes of the FADC used in the Test run.}
%\label{fig:hps_trigger_data}
%}
%\end{center}
%\end{figure}

@@

The trigger system is designed to select time coincidences of electromagnetic clusters in the 
top and bottom halves of the ECal. Figure~\ref{fig:hps_trigger_cal} shows a schematic overview 
of each stage of the system. 
 \begin{figure}[b]
\begin{center}
{\small
 \includegraphics[width=8cm]{figures/hps_trigger_cal}
\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
signals for each detector channel and sends them for cluster finding in the CTP. The CTP clusters are 
sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the 
ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout 
the sub-detectors.}
 \label{fig:hps_trigger_cal}
}
\end{center}
 \end{figure}
Each channel on the FADC board has an independent data path to send 5-bit pulse energy and 3-bit 
pulse arrival time information every 32~ns to a trigger processing board (CTP), which is in the same 
crate. The 3-bit pulse arrival time allows the trigger to know the pulse timing at 4~ns resolution. 
Contrary to the readout path 
described in Sec.~\ref{sec:fadc}, this energy is a pedestal subtracted time-over-threshold sum with 
programmable offsets and minimum threshold discriminator for each channel. With input from all 
FADC channels, i.e. one half of the ECal, the CTP performs cluster finding and calculates cluster 
energy, shape and timing information. The 3x3 fixed-window, highly parallel, FPGA-based cluster 
algorithm simultaneously searches for up to 125 clusters with energy sum larger than 
the programmable energy threshold ($\approx270$~MeV). Crystals in the 
fixed-window are included in the sum if the leading edge of the pulse occurred within a 32~ns time 
window to take into account clock skew and jitter throughout the system.
The CTP only accepts clusters with the highest energy 3x3 window locally to deal with overlapping and 
very large clusters. The sub-system board (SSP) receives the clusters from the top and bottom half CTP 
at a maximum of 250MHz and searches for pairs of clusters in a 8 ns wide coincidence window. The 
SSP sends triggers to the trigger supervisor (TS), which generates all the necessary signals and 
controls the entire DAQ system readout through the trigger interface units installed in every crate that 
participate in the readout process.

@@

The integrated pulse of each FADC channel was converted to energy by  
subtracting a pedestal and apply a conversion factor to convert ADC counts to energy. 
The pedestals are measured using special runs where each trigger records 100 samples of signals 
from the APDs with 4~ns between each sample. The pedestals were extracted from the 
part of the window before the actual hit in the calorimeter. Modules with signal above the threshold  
are clustered using a simple algorithm similar to the one 
deployed for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective readout threshold of 
73~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering 
algorithm worked well for reconstruction of the detected shower energy. An average noise level of 
approximately 15~MeV was measured in special pedestal runs.

The ratio of the ECal cluster energy $E$ to the momentum $p$ of a matched track in the SVT was used 
to determine the conversion factors from ADC counts to energy. To compare data and simulation, all 
inoperable or noisy channels in the SVT and ECal were disabled in both data and simulation so that 
any efficiency or bias that affect the data should be reflected in the simulation. 
%Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel. 
%simulation to those observed in data by comparing .  The ``weighted $E/p$'' for each crystal is %computed, 
%representing the average $E/p$ for clusters that include the crystal
% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
Iteratively, conversion coefficients for each crystal were adjusted until the $E$/$p$ ratio in data and 
simulation were similar. The distribution of the $E$/$p$ ratio in data and simulation are compared in 
Fig.~\ref{fig:gains}. 
{\small
\begin{figure}[]
\begin{center}
	\includegraphics[width=7cm]{figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.pdf}
	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation 
	for single cluster triggers in the top half of the ECal.} 
	\label{fig:gains}
\end{center}
\end{figure}
}
The peak position of the distribution indicates the sampling fraction of the ECal, the fraction of the 
incident particle energy measured in the cluster. The width and tails of the distribution 
in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
agreement with simulation was found to be sufficient to study normalized event rates on the Test run.

@@

\section{Acknowledgements}
The authors are grateful for the support from Hall~B at JLab and especially Hall~B technicians 
for support during installation and decommissioning. They also would like to commend the CEBAF 
personnel for achieving good performance when we needed it; the last few hours of operating CEBAF6. 
The tremendous support from home institutions and supporting staff also needs praise from the authors.

>>>>

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at energies of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in a final state particle within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam enlarges downstream after multiple scattering in the target and electrons 
which have radiated in the target disperse horizontally in the field of the analyzing magnet. Together 
they constitute a "wall of flame" which must be completely avoided. Accordingly, 
the apparatus is split vertically to avoid a "dead zone", the region within $\pm 15$~mrad of the beam 
plane. In addition, the beam is transported in vacuum through the tracker to minimize beam-gas 
interaction backgrounds. Even with these precautions, the occupancies of sensors near the beam 
plane are high, dominated by the
multiple Coulomb scattering of the primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
The trigger comes from a highly-segmented  PbWO$_{4}$ crystal calorimeter located just downstream 
of the dipole magnet. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

The silicon tracking and vertexing detector for HPS Test, or SVT, resides in a vacuum 
chamber inside the Pair Spectrometer (PS) dipole magnet in Hall B at JLab. The SVT has five 
measurement stations, or ``layers,'' beginning10 cm downstream of the target. Each layer 
comprises a pair of closely-spaced silicon microstrip sensors responsible for measuring a single 
coordinate, or ``view.'' Introduction of a small (50 or 100~mrad) stereo angle between the two 
sensors of each layer provides three-dimensional tracking and vertexing throughout the acceptance 
of the detector. In order to accommodate the dead zone, the 
SVT is built in two halves that are approximately mirror reflections of one another about the plane of the 
nominal electron beam.  Each layer in one half is supported on a common support plate with 
independent cooling and readout.

@@

\section{The HPS Test Run Beamline}
The HPS Test run studied multiple Coulomb scattering of electrons and positrons from 
bremsstrahlung photons produced in the Hall B tagged photon facility. 
Figure~\ref{fig:hpstest_layout} shows the layout of 
the setup on the beam line. The SVT was installed inside the Hall B pair 
spectrometer magnet vacuum chamber with the ECal mounted downstream of it. Both the 
SVT and the ECal were retracted off the beam plane compared to nominal electron beam runing to 
allow clean passage of the photon beam through the system. 
\begin{figure}[]
    \includegraphics[width=0.5\textwidth]{figures/HPS_dimensions}
\caption{\small{Layout of the HPS parasitic run.} }
\label{fig:hpstest_layout}
\end{figure}

The photon beam was generated in the interaction of $5.5$~GeV electrons with a $10^{-4}~X_0$ 
gold radiator located $\approx~9$~m upstream of the PS. The primary beam and scattered 
electrons are deflected away from detectors by the dipole magnet of the photon tagging system. 
During the dedicated HPS Test run period, the collimated (6.4~mm diameter), photon beam passes 
through the gold PS pair converter and later the HPS system as illustrated in 
Fig.~\ref{fig:schematic_testrun_vs_erun}.
\begin{figure}[]
\includegraphics[ width=7cm]{figures/photon_vs_electron_beam_schematic.png}
\caption{\small{Illustrative comparison of HPS Test run photon beam compared to the HPS electron 
beam.}}
\label{fig:schematic_testrun_vs_erun}
\end{figure}
The PS pair converter was located $\approx~77$~cm upstream of the first layer of the SVT.

@@

The ECal module shown in Fig.~\ref{fig:ecal-module} is based on a tapered 160~mm long 
lead-tungstate (PbWO$_{4}$) crystal with a $13.3\times13.3$~mm$^2$ ($16\times16$~mm$^2$) front 
(rear) face wrapped in VM2000 multilayer polymer mirror film. 
\begin{figure}[]
\begin{center}
{\small
\includegraphics[width=7cm]{figures/ecal-module-schematic.png}
\caption{Schematic vied of an ECal module.}
\label{fig:ecal-module}
}
\end{center}
\end{figure}
The scintillation light, approximately $3$ photoelectrons/MeV, is readout by a 
5$\times$5~mm$^2$ Hamamatsu S8664-55 Avalanche Photodiode (APD) with 75\% quantum 
efficiency glued to the rear face surface using MeltMount 1.7 thermal plastic adhesive. 
The low gain of APDs ($\sim 200$) was compensated with custom made preamplifier boards, which 
provide factor of $2600$ amplification of the APD signal.

\subsection{Layout}
Similar to the SVT, the ECal is built in two separate halves that are mirror reflections of one another 
about the plane of the nominal electron beam to avoid interfering with the 15~mrad "dead zone". 
As shown in Fig.~\ref{fig:ecal}, the 221 modules in each half, supported by aluminum support frames, 
are arranged in rectangular formation with 5 layers and 46 crystals/layer except for the layer closest to 
the beam where 9 modules were removed to allow a larger opening for the outgoing electron and 
photon beams. Each half was enclosed in a temperature controlled box ($<1^{\circ}$~F stability and 
$<4^{\circ}$~F uniformity) to stabilize the crystal light yield and the operation of the APDs and its 
preamplifiers. 
Four printed circuit boards mounted on the backplane penetrated the enclosure and was used to 
supply the $\pm 5$~V operating voltage for the preamplifiers, 400~V bias voltage to the APDs, and to 
read out signals from the APDs. Each half of the ECal was divided into 12 bias voltage groups with a 
gain uniformity of about 20\%.

@@

\subsection{Signal readout}
\label{sec:fadc}
After a 2:1 signal splitter, $1/3$ of an amplified APD signal is fed to a 
single channel of a JLab flash ADC (FADC) board~\cite{fadc}. $2/3$ of the signal is sent to a 
discriminator module and then to a TDC for a timing measurement. 
%\begin{figure}[]
%\begin{center}
%{\small
%\includegraphics[width=4cm]{figures/FADC250_Photo_001.jpg}
%\caption{The JLab FADC250 VXS module.}
%\label{fig:fadc}
%}
%\end{center}
%\end{figure}
The FADC boards are high speed VXS modules digitizing up to 16 APD signals 
at 250~MHz and storing samples in 8~$\mu$s deep pipelines with 12-bit resolution. 
When a trigger is received, the part 
of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
threshold (for the Test run this was set to $\approx70$~MeV) are 
summed and stored in a 17-bit register for readout. In addition a 4~ns resolution timestamp of the 
threshold crossing is reported in the readout for each pulse.
This scheme significantly compresses the data output of the FADC. During offline data analysis, a 
calibrated pedestal value is subtracted to obtain the actual summed energy.
Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test run to read out the top 
(bottom) half of the ECal.
In the Test run 385 out of 442 modules (87\%) were used in offline reconstruction, 39 modules were 
disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
excessive noise) and 18 were masked offline due to noise. 
%\begin{figure}[]
%\begin{center}
%{\small
%\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
%\caption{The two different readout modes of the FADC used in the Test run.}
%\label{fig:hps_trigger_data}
%}
%\end{center}
%\end{figure}

@@

The trigger system is designed to select time coincidences of electromagnetic clusters in the 
top and bottom halves of the ECal. Figure~\ref{fig:hps_trigger_cal} shows a schematic overview 
of each stage of the system. 
 \begin{figure}[b]
\begin{center}
{\small
 \includegraphics[width=8cm]{figures/hps_trigger_cal}
\caption{Block diagram of the ECAL trigger system consisting of the FADC that samples and digitizes 
signals for each detector channel and sends them for cluster finding in the CTP. The CTP clusters are 
sent to the SSP where the final trigger decision is taken based on pairs of clusters in both halves of the 
ECal. The decision is sent to the Trigger Supervisor (TS) that generates the necessary signals to readout 
the sub-detectors.}
 \label{fig:hps_trigger_cal}
}
\end{center}
 \end{figure}
Each channel on the FADC board has an independent data path to send 5-bit pulse energy and 3-bit 
pulse arrival time information every 32~ns to a trigger processing board (CTP), which is in the same 
crate. The 3-bit pulse arrival time allows the trigger to know the pulse timing at 4~ns resolution. 
Contrary to the readout path 
described in Sec.~\ref{sec:fadc}, this energy is a pedestal subtracted time-over-threshold sum with 
programmable offsets and minimum threshold discriminator for each channel. With input from all 
FADC channels, i.e. one half of the ECal, the CTP performs cluster finding and calculates cluster 
energy and timing information. The 3x3 fixed-window, highly parallel, FPGA-based cluster 
algorithm simultaneously searches for up to 125 clusters with energy sum larger than 
the programmable energy threshold ($\approx270$~MeV). Crystals in the 
fixed-window are included in the sum if the leading edge of the pulse occurred within a 32~ns time 
window to take into account clock skew and jitter throughout the system.
The CTP only accepts clusters with the highest energy 3x3 window locally to deal with overlapping and 
very large clusters. The sub-system board (SSP) receives the clusters from the top and bottom half CTP 
at a maximum of 250MHz and searches for pairs of clusters in a 8 ns wide coincidence window. The 
SSP sends triggers to the trigger supervisor (TS), which generates all the necessary signals and 
controls the entire DAQ system readout through the trigger interface units installed in every crate that 
participate in the readout process.

@@

The integrated pulse of each FADC channel was converted to energy by  
subtracting a pedestal and applying a conversion factor to convert ADC counts to energy. 
The pedestals are measured using special runs where each trigger records 100 samples of signals 
from the APDs with 4~ns between each sample. The pedestals were extracted from the 
part of the window before the actual hit in the calorimeter. Modules with signal above the threshold  
are clustered using a simple algorithm similar to the one 
deployed for the trigger (see Sec.~\ref{sec:trigger}). Due to the high effective readout threshold of 
73~MeV the average number of crystals in a cluster was $\sim 3$ and the simple clustering 
algorithm worked well for reconstruction of the detected shower energy. An average noise level of 
approximately 15~MeV was measured in special pedestal runs.

The ratio of the ECal cluster energy $E$ to the momentum $p$ of a matched track in the SVT was used 
to determine the conversion factors from ADC counts to energy. To compare data and simulation, all 
inoperable or noisy channels in the SVT and ECal were disabled in both data and simulation so that 
any efficiency or bias that affect the data should be reflected in the simulation. 
%Furthermore, a conversion factor calibration is performed to equalize the gains of  each channel. 
%simulation to those observed in data by comparing .  The ``weighted $E/p$'' for each crystal is %computed, 
%representing the average $E/p$ for clusters that include the crystal
% $\frac{\sum_j w_{j,i}}{\sum_j\frac{P_j}{E_j}w_{j,i}}$.
Iteratively, conversion coefficients for each crystal were adjusted until the $E$/$p$ ratio in data and 
simulation were similar. The distribution of the $E$/$p$ ratio in data and simulation are compared in 
Fig.~\ref{fig:gains}. 
{\small
\begin{figure}[]
\begin{center}
	\includegraphics[width=7cm]{figures/h_ep_data_0_h_ep_MC_0_dataMC_1351-v6-v6gains_2-trig-top-cl600reg0.pdf}
	\caption{The ECal energy over track momentum ratio ($E$/$p$) comparing data and simulation 
	for single cluster triggers in the top half of the ECal.} 
	\label{fig:gains}
\end{center}
\end{figure}
}
The peak position of the distribution indicates the sampling fraction of the ECal, the fraction of the 
incident particle energy measured in the cluster. The width and tails of the distribution 
in data indicates imperfect calibration and noise of the ECal modules. This level of calibration and the 
agreement with simulation was found to be sufficient to study normalized event rates in the Test run.

@@

\section{Acknowledgements}
The authors are grateful for the support from Hall~B at JLab and especially the Hall~B engineering 
group for support during installation and decommissioning. They also would like to commend the 
CEBAF personnel for good beam performance; the last few hours of operating CEBAF6. 
The tremendous support from home institutions and supporting staff also needs praise from the 
authors.
